---
title: "LNRS Wetlands"
format:
  html:
    theme: sandstone
    toc: true
    toc-depth: 3
    toc-location: right
    number-sections: true
    callout-icon: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, echo=FALSE, cache=TRUE)
```

## Dorset LNRS Viewer Data Analysis

Here we review data within the Dorset LNRS Data Explorer, this exercise is pre-public consultation. 

The Local Habitat Map (main mapping output of the LNRS) is accessible in the [Dorset LNRS Explorer](https://gi.dorsetcouncil.gov.uk/dorsetexplorer/nature-recovery#map=14.60/50.67895/-2.13060/0&basemap=9/100/100)

Within the LNRS "potential activies" layer here we see the potential measures which are proposed for nature recovery.
```{r}
library(sf)
library(leaflet)
library(magrittr)
library(tidyverse)

# Get outline of Dorset Local Authority/LNRS boarder
LA <- read_sf("/dbfs/mnt/base/unrestricted/source_ons_open_geography_portal/dataset_local_authority_districts_bdy_uk_bfe/format_SHP_local_authority_districts_bdy_uk_bfe/LATEST_local_authority_districts_bdy_uk_bfe/local_auth_dist_bdy_uk_bfe.shp") %>% 
  filter(LAD24NM == "Dorset") %>% 
    st_transform(4326)

PA <- read_sf("/dbfs/FileStore/WSX_HGray/Potential_Activities.gpkg") %>% 
  st_transform(4326)

# Load Detailed river network & crop to Dorset
DRN <- read_sf("/dbfs/mnt/lab/unrestricted/harry.gray@environment-agency.gov.uk/DRN/DRN_Merged_MCAT.shp") 

DRN <- DRN[LA,]

Chalk <- read_sf("/dbfs/FileStore/WSX_HGray/Chalk_streams_Dorset.shp") %>% 
            st_transform(4326)


PAL <- colorFactor(palette = c("#FBE183", "#F5CC2F", "#F8B108" ,"#F78C09", "#DC4D35" ,"#B23A3F" ,"#B14054" 
                               ,"#DE5A7C" ,"#E57386" ,"#E78E97" ,"#AD7CA1"
                               ,"#874884", "#1f6e9c", "#2A6495" , "#2b9b81" ,"#92c051","#92C051" ,"#47A573"),
                   levels = PA$primary_activities)


# Filter just for heathland sites
PA <- PA %>% group_by(primary_activities) %>% 
  mutate(occurance_Prim_Act = n(),
         Total_area = sum(as.numeric(area))) %>% 
  ungroup() %>% 
  group_by(river_activities) %>% 
  mutate(occurance_riv_act= n(),
         Total_riv_area = sum(as.numeric(area))) %>% 
  ungroup()
  
```


### Primary Activities 

The below plot shows Primary Activites within Dorset to provide a flavour of primary activities. Below is a plot of secondary activities. Note there are no river or "riparian" activies as primary activities.

```{r}
library(plotly)
library(MetBrewer)

a <- ggplot(PA, aes(y = reorder(primary_activities, +table(primary_activities)[primary_activities]), fill = primary_activities)) +
  geom_bar() +
  scale_fill_manual(values = met.brewer("Tsimshian", 19)) +  # Use scale_fill_manual instead of scale_color_manual
  labs(y = "Primary Activities (Sorted)", x = "Count") +
  theme_minimal()+
  theme(legend.position = "none")

a
```

:::{.column-page}
```{r Leaflet Map of Wetlands}


PA_W <- PA %>% 
  filter(primary_activities %in% c("create or enhance wetland habitat","enhance wetland habitat", "create or enhance heathland or wetland habitat" ))


  
  ggplot() +
  geom_sf(data = PA_W, aes(fill = "salmon")) +
    geom_sf(data = DRN, col = "steelblue")+
    geom_sf(data= LA, fill=NA)+
  theme_void()


```
:::