---
title: "LNRS Rivers"
format:
  html:
    theme: sandstone
    toc: true
    toc-depth: 3
    toc-location: right
    number-sections: true
    callout-icon: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, echo=FALSE, cache=TRUE)

library(sf)
library(leaflet)
library(magrittr)
library(tidyverse)

LA <- read_sf("/dbfs/mnt/base/unrestricted/source_ons_open_geography_portal/dataset_local_authority_districts_bdy_uk_bfe/format_SHP_local_authority_districts_bdy_uk_bfe/LATEST_local_authority_districts_bdy_uk_bfe/local_auth_dist_bdy_uk_bfe.shp") %>% 
  filter(LAD24NM == "Dorset") %>% 
    st_transform(4326)
# Load Detailed river network & crop to Dorset
DRN <- read_sf("/dbfs/mnt/lab/unrestricted/harry.gray@environment-agency.gov.uk/DRN/DRN_Merged_MCAT.shp") 

DRN <- DRN[LA,]

Chalk <- read_sf("/dbfs/FileStore/WSX_HGray/Chalk_streams_Dorset.shp") %>% 
            st_transform(4326)

```

#### Potential River Measures Dorset LNRS

The below map includes all river measures, these include the below activities, sites can have multiple proposed activities as a mixture of the below: 

* Potential to reduce nutrient run-off through habitat creation or enhancement.
* Increase or enhance riparian planting
* Enhance priority river habitat
* Potential to improve river water quality and ecological condition

```{r}
PA <- read_sf("/dbfs/FileStore/WSX_HGray/Potential_Activities.gpkg") %>% 
  st_transform(4326)

PAR <- PA %>% 
  filter(!(river_activities %in% c("","NA")))



  ggplot() +
   geom_sf(data = DRN, fill = "red", col = "red")+
  geom_sf(data = PAR, fill = "orange", col = "green")+
  theme_void()

```

